Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Typos

\section{Application: Finding completions of underconstrained glassy structures to isostatic}
\label{sec:bodypin}

We can use DR-plans to help in solving questions in designs for graphene and silica bilayers (\todo{Add Citation}). Specifically, we will look into the problem when you have a monolayer and it is underconstrained. Our goal is to make such a layer isostatic. This can be done in a number of ways.

@@

\begin{enumerate}
    \item Pin together 2 underconstrained monolayers in such a way that the resulting bilayer becomes isostatic (see Figure \ref{fig:silica_glass}).
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Build the structures by repeated subdivision to ensure they are isostatic at each layer (see Figure \ref{fig:subdivision})
\end{enumerate}

We will discuss item 2 in detail in this section. In each case, we are specifically interested in how to they can be applied to get a resulting isostatic structure with a small DR-plan, so a realization can be found quickly. To answer these questions, we first inroduce the structures we model the problems with:

@@

\begin{definition}
    A \emph{body-hyper-pin qusec} is a qusec where the obejct are rigid bodies that are pinned together by some number of pins.
\end{definition}

@@

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR-plan, we treat each body as trivial, so they become the leaves of our plan. The optimal completion problem and approach of Section \ref{sec:DRP} are unchanged. The optimal paramaterization problem in Section \ref{sec:DRP} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

For the rest of this section, we will only be dealing with the DR-pla n of such qusecs. As such, we will refer only to the underlying graph of the qusecs. We now go over 2 subclasses of body-hyper-pin graphs for modeling Examples 4 and 5 in Section \ref{sec:intro}.

@@

Body-pin graphs are of particular interest to us in the context of Example 4 in Section \ref{sec:intro}. Multi-triangle-pin graphs can be used to reprsent the silica bi-layers and glassy structures described in Example 5 of Section \ref{sec:intro}, where each triangle is the junction of ``disks'' in the plane (se Figure \ref{fig:silica_glass}). Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR-plan:

\begin{definition}
    A \emph{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

@@

    \begin{itemize}
        \item Its children will be 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph
        \item Its children will be a number of proper maximal 1-dof subgraphs, joined pairwise by at most one pin
    \end{itemize}
\end{observation}

@@

    For item 2, consider the case where we have more than 2 proper vertex maximal 1-dof subgraphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \cup k_j$ would be $(3,4)$-tight and hence $k_i$ and $k_j$ are not vertex maximal.
\end{proof}

@@

\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or multi-triangle graph $G$ and correpsonding 1-dof DR plan $T$, there is a quadratic algorithm for the 1-dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin graphs.
\end{theorem}

\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof subgraph of $G$.

    To make the graph isostatic, we need only add one body and pin it to 2 other bodies. Doing so will cause $G$ to become $(3,3)$-tight. We choose the 2 boodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a subgraph. We pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.

@@

    For each node $b$, we assign a size of the $T_b$ denoted $|T_b|$. $|T_b| = \displaystyle\max_{v \in T_b} fanin(v)$. We are looking for $b$ that minimizes $|T_b|$. Denote the subtree of $T$ rooted at $v$ by $T^v$ and the number of leaves in a tree $T$ by $nl(T)$. Note that $fanin(b)= nl(T^b)$ because no descendent of $b$ is isostatic. Similarly, for any ancestor $w$ of $b$, $fanin(w) = nl(T^w)-nl(T^{b'})+1$, where $b'$ is the child leading to $b$. All other nodes are not isostatic and so have no fanin.

>>>>

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}

We can use DR-plans to help in solving questions in designs for graphene and silica bi-layers (\todo{Add Citation}). Specifically, we will look into the problem when you have a mono-layer and it is under-constrained. Our goal is to make such a layer isostatic. This can be done in a number of ways.

@@

\begin{enumerate}
    \item Pin together 2 under-constrained mono-layers in such a way that the resulting bi-layer becomes isostatic (see Figure \ref{fig:silica_glass}).
    \item Pin the boundary in such a way that the resulting system is isostatic.
    \item Build the structures by repeated subdivision to ensure they are isostatic at each layer (see Figure \ref{fig:subdivision})
\end{enumerate}

We will discuss item 2 in detail in this section. In each case, we are specifically interested in how to they can be applied to get a resulting isostatic structure with a small DR-plan, so a realization can be found quickly. To answer these questions, we first introduce the structures we model the problems with:

@@

\begin{definition}
    A \emph{body-hyper-pin qusec} is a qusec where the object are rigid bodies that are pinned together by some number of pins.
\end{definition}

@@

\begin{proof}
    We can replace each body that has only one pin by a single vertex. A body with 2 pins can be replaced by an edge. In general, a body with $n$ pins can be replaced by a 2-tree on $n$ vertices. When looking for a DR-plan, we treat each body as trivial, so they become the leaves of our plan. The optimal completion problem and approach of Section \ref{sec:DRP} are unchanged. The optimal parameterization problem in Section \ref{sec:DRP} now has an additional constraint that all edges in the 2-tree representation of the bodies must be removed together, not individually.
\end{proof}

For the rest of this section, we will only be dealing with the DR-plan of such qusecs. As such, we will refer only to the underlying graph of the qusecs. We now go over 2 sub-classes of body-hyper-pin graphs for modeling Examples 4 and 5 in Section \ref{sec:intro}.

@@

Body-pin graphs are of particular interest to us in the context of Example 4 in Section \ref{sec:intro}. Multi-triangle-pin graphs can be used to represent the silica bi-layers and glassy structures described in Example 5 of Section \ref{sec:intro}, where each triangle is the junction of ``disks'' in the plane (see Figure \ref{fig:silica_glass}). Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR-plan:

\begin{definition}
    A \emph{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

@@

    \begin{itemize}
        \item Its children will be 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph
        \item Its children will be a number of proper maximal 1-dof sub-graphs, joined pairwise by at most one pin
    \end{itemize}
\end{observation}

@@

    For item 2, consider the case where we have more than 2 proper vertex maximal 1-dof sub-graphs $s_1, ..., s_k, k > 2$. Then, if $k_i$ and $k_j$ are joined by $2$ pins, $k_i \cup k_j$ would be $(3,4)$-tight and hence $k_i$ and $k_j$ are not vertex maximal.
\end{proof}

@@

\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or multi-triangle graph $G$ and corresponding 1-dof DR plan $T$, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb} for body-pin and multi-triangle-pin graphs.
\end{theorem}

\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof sub-graph of $G$.

    To make the graph isostatic, we need only add one body and pin it to 2 other bodies. Doing so will cause $G$ to become $(3,3)$-tight. We choose the 2 bodies to pin to by choosing a node $b$ in $T$ and looking at its children. From Observation \ref{rem:1dofcanon}, we know that the children can only be joined by a single pin or a sub-graph. We pin the new body to bodies in two separate children. Doing so will ensure that all children of $b$ will have 1-dof and all ancestors of $b$ (including $b$) will now be isostatic.

@@

    For each node $b$, we assign a size of the $T_b$ denoted $|T_b|$. $|T_b| = \displaystyle\max_{v \in T_b} fanin(v)$. We are looking for $b$ that minimizes $|T_b|$. Denote the sub-tree of $T$ rooted at $v$ by $T^v$ and the number of leaves in a tree $T$ by $nl(T)$. Note that $fanin(b)= nl(T^b)$ because no descendant of $b$ is isostatic. Similarly, for any ancestor $w$ of $b$, $fanin(w) = nl(T^w)-nl(T^{b'})+1$, where $b'$ is the child leading to $b$. All other nodes are not isostatic and so have no fanin.
